Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Editing on analysis method.

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of various scenarios (i.e., the percentage of participants who reported a `5' on the Likert scales), rather than the average of all Likert scores. We did this for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission). Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is if they were maximally upset or not, rather than how upset they were. In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not heavily impacted by outliers. Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses and had an initial agreement rate of 89.7\%. The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

>>>>

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales.
We use the VUR rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, we believe that everyone would be upset, at least a little, at the given scenarios (i.e., in all scenarios, the device takes action without permission). Thus, we believe that the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.

In the risk/benefit section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not heavily impacted by outliers. Finally, for the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%. The researchers discussed any disagreements and resolved them so that the final codings reflect unanimous agreement.
